```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## How to merge the files

```{r}
library(tidyverse)
library(data.table)
```

Place `brgy_info.csv` in the desired folder and use `data.table::fread` for faster import.  The precinct level votes are found in the `votes2.csv` file. See the Dictionary of Terms section to learn more about the columns of the `votes2.csv` file.  The `contest.csv` file contains the ballot order (`bo`), which can be matched with the `boc` column in the `brgy_master.csv`.

```{r}
# import the files
brgy_master <- fread("./data/processed/brgy_info.csv")
votes <- fread("./data/processed/votes2.csv")
contest <- fread("./data/processed/contest.csv")

# say for example you want to import all votes for senators
senators <- contest[ccn == "SENATOR"]
senators <- senators %>% left_join(votes, by = c("boc"="bo", "cc"))

# remove the unneeded objects if you don't have enough memory
# the resulting file sizes are quite large
# rm(contest)
# rm(votes)

senators <- senators %>% left_join(brgy_master, by = "vbc")

# export the senators object into a csv file
fwrite(senators, "./data/processed/senators_brgy.csv")
```

The file `info.R` is used to extract the information from the `info.json` files into `csv` files. The file `coc.R` is used to extract the information from the `coc.json` files into `csv` files. 

## Dictionary of terms

* `boc` ballot order in the coc
* `bon` ballot order name; the name of the contestant
* `boi` ballot order (index?)
* `to`                   
* `pc`                   
* `pn` party name                   
* `pcc`                   
* `pcy`                  
* `pcm`                   
* `pck`                  
* `type.x` level of governance              
* `pre.x`                
* `ccn` position aspired for
* `ccc`                  
* `cn` position aspired for                    
* `cc`                   
* `v` number of votes at the precinct level                     
* `tot` total number of votes cast             
* `per` percent of votes based on `tot`                  
* `ser`                  
* `vbc` vote barangay code
* `rc`                   
* `rcc`                   
* `rn`                   
* `can`                   
* `cll`                  
* `cl`                    
* `url`                  
* `total-vb`              
* `total-voters` total registered voters in the barangay       
* `ppc`                   
* `ppcc` barangay/municipal/provincial code                 
* `ppn` name of barangay/municipality/province       
* `pre.y`                
* `cpre`  precinct codes                
* `url1`                 
* `type.y`                
* `rccm` municipal code                
* `rccp` provincial code                  
* `municipality` name of the municipality         
* `province` name of the province              
* `Name` name of barangay/municipality/province[^1]                
* `Inter-Level` administrative levels: barangay, municipal, etc
* `City Class` City class
* `Income Classification` 1, 2, 3, 4, 5 
* `Urban/Rural` 
* `rccr` region code          
* `region` region name

[^1]: https://psa.gov.ph/classification/psgc/